Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-24 WSSSPE2_report/WSSSPE2_review.tex
Section 3.2: Fixed compilation errors.

Hong led the audience to ponder on the questions that if 92\% of researchers and WSSSPE
care about scientific software, what are we going to \emph{do} to help researchers and 
to achieve software sustainability?
\begin{comment}
With apologies to Greg Wilson:
\href{http://software-carpentry.org/blog/2013/10/you-keep-using-that-word.html}
{You Keep Using That Word}
We can talk all day about the best ways of achieving sustainability
But what are we going to do to make it actually sustainable?
\end{comment}
Careers outside academic sector: 
Non-university Research (industry, government, etc.)

UK STEM graduate career paths: Early Career Research, Permanent Research Staff,
Professor

\begin{comment}
Source: The Scientific Century, Royal Society, 2010 (revised to reﬂect ﬁrst stage
clariﬁcaFon from ``What Do PhD’s Do?'' study)

Who	are	the	people 	we	need to	persuade?
What		are	the	incentives 	we need 	to	put 	in	place?
How are we going to show that the work we present here has benefit to the 92\%?

We	are	all	the 92\%	and	we can	change	the world	if	we	want!

\url{http://dx.doi.org/10.6084/m9.ﬁgshare.1243288}
\end{comment}

>>>>

Hong led the audience to ponder the questions of what we are going to \emph{do}
to help researchers and to achieve software sustainability if 92\% of
researchers and WSSSPE care about scientific software.
\begin{comment}
With apologies to Greg Wilson:
\href{http://software-carpentry.org/blog/2013/10/you-keep-using-that-word.html}
{You Keep Using That Word}
We can talk all day about the best ways of achieving sustainability
But what are we going to do to make it actually sustainable?
\end{comment}
Careers outside academic sector: 
Non-university Research (industry, government, etc.)
UK STEM graduate career paths: Early Career Research, Permanent Research Staff,
Professor.
The Scientific Century, Royal Society, 2010 (revised to reflect first stage
clarification from ``What Do PhD's Do?'' study.)
Who	are the people  we need to persuade?
What	 are	the incentives we need to put in place?
How are we going to show that the work we present here has benefit to the 92\%?
We are all the 92\%	and we can change the world if we	want!
